Agreement Attraction in Turkish: Effects of Nominal and Verbal Plural Morphemes

### 2019-02-13 Paper/AgreementAttraction.Rmd
First model, and major restructuring of the directory structure.

author:

- name: Utku Turk
  affilnum: 1
  email: utku.turk@boun.edu.tr

- name: Pavel Logacev 
  affilnum: 1

affiliation:

- affilnum: 1
  affil: Bogazici University, Department of Linguistics, Istanbul, Turkey

output:

  pdf_document:
    fig_caption: yes
    fig_width: 7
    fig_height: 7
    keep_tex: yes
    number_sections: yes
    template: manuscript.latex
    includes:
      in_header: header.tex

  html_document: null

  word_document: null

documentclass: article
classoption: a4paper
capsize: normalsize
fontsize: 11pt
geometry: margin=1in
linenumbers: no
spacing: singlespacing
footerdate: yes
bibliography: 
  - references.bib
  - knitcitations.bib
csl: ecology.csl

---

```{r setup, include=FALSE, cache=FALSE, message = FALSE}

library("knitr")

#opts_knit$set(root.dir=normalizePath('../'))

### Chunk options: see http://yihui.name/knitr/options/ ###

## Text results
opts_chunk$set(echo = TRUE, warning = TRUE, message = TRUE, include = TRUE)

## Code decoration
opts_chunk$set(tidy = TRUE, comment = NA, highlight = TRUE)

## Cache
opts_chunk$set(cache = 2, cache.path = "output/cache/")

## Plots
opts_chunk$set(fig.path = "output/figures/")

@@

```{r knitcitations, echo=FALSE, cache = FALSE}
library(knitcitations)
cleanbib()   
cite_options(citation_format = "pandoc")
```

```{r init, message=FALSE, warning=FALSE, include=FALSE, paged.print=FALSE}
library(languageR)
library(tidyverse)
library(gdata)
library(MASS)
library(magrittr)
library(ggplot2)

data <- read.csv('results', 
                 header = F, 
                 comment.char = "#", 
                 encoding = "UTF-8" , 
                 col.names = paste0("V",seq_len(11)), 
                 fill = TRUE)

colnames(data) = c("Time", "MD5", "ControllerType", "SentenceNoInStimFile", "Element", "Type", "Item", "Sentence", "Question","Answer", "RT")

FormEntries <- subset(data, ControllerType != "DashedAcceptabilityJudgment" ) %>% drop.levels(); nrow(data)
data %<>% subset(ControllerType == "DashedAcceptabilityJudgment")
age <- dplyr::select(FormEntries, MD5,Sentence,Question) %>% 
  dplyr::filter(Sentence == "age") %>%
  dplyr::select(MD5, Age = Question)
natturk <- dplyr::select(FormEntries, MD5,Sentence,Question) %>% 
  dplyr::filter(Sentence == "natturk") %>%
  dplyr::select(MD5, Natturk = Question) %>%
  mutate(Natturk = Natturk == "male")
dex <- dplyr::select(FormEntries, MD5,Sentence,Question) %>% 
  dplyr::filter(Sentence == "dex") %>%
  dplyr::select(MD5, Dex = Question) %>%
  mutate(Dex = ifelse(Dex == "male", "right-handed", "left-handed"))
FormPart <- dplyr::left_join(age, natturk, by = "MD5") %>% 
  dplyr::left_join(., dex , by = "MD5" ) %>% 
  unique()
lenForm <- length(levels(factor(FormPart$MD5))); lenForm
md5form <- levels(factor(FormPart$MD5))
md5form_subject <- data.frame("MD5" = md5form, "Subject" = sprintf("S[%s]",seq((lenForm))))
FormPart <- merge(FormPart,md5form_subject, all = T)

stopifnot( nrow(data) %% 2 == 0 )
rows_stim <- data[c(T,F),]
rows_resp <- data[c(F,T),]

data <- rows_resp %>% left_join(md5form_subject) %>% dplyr::select(-MD5, -Time, -ControllerType, -Sentence, -Element) %>%
  dplyr::rename(ResponseCorrect=Answer, Response=Question)
data %<>% group_by(Subject) %>% mutate(trial_no = seq(Subject))
data %<>% within({ late_response = (Response == "NULL")
Response[late_response] = NA
ResponseCorrect[late_response] = NA
})

responses <- c(yes="İYİ (P'ye basınız)", no="KÖTÜ (Q'ya basınız)")
stopifnot( all(data$Response %in% responses | is.na(data$Response) ) )

data$ResponseYes <- ifelse(grepl("P",data$Response) , T, 
                           ifelse(grepl("Q",data$Response) , F, NA))

data$condition <- 
  with(data, case_when(Type == "filler" & SentenceNoInStimFile >= 200 ~ "a",
                       Type == "filler" & SentenceNoInStimFile < 200 ~ "b",
                       Type == "condition_a" ~ "a",
                       Type == "condition_b" ~ "b",
                       Type == "condition_c" ~ "c",
                       Type == "condition_d" ~ "d",
                       TRUE ~ as.character(NA)))
data$experiment <- ifelse(data$Type %in% c("condition_a", "condition_b", "condition_c", "condition_d"), "AgrAttr", as.character(data$Type))

data %>% group_by(experiment, condition) %>% 
  summarise(perc_yes = mean(ResponseYes, na.rm = T),
            perc_na = mean(is.na(ResponseYes)))

conditions_info <- data.frame(experiment = c("AgrAttr", "AgrAttr", "AgrAttr", "AgrAttr", "filler", "filler"),
                              condition = c("a","b","c","d", "a","b"),
                              grammatical = c("ungram", "gram", "ungram", "gram", "ungram", "gram"),
                              verb_num = c("sg","pl","sg","pl", "sg","pl"),
                              attracted = c(T,T,F,F,F,F),
                              stringsAsFactors = FALSE) 
data %<>% left_join(conditions_info)
data %<>% subset(Type != "practice") %>% drop.levels()

dataAv <- data %>% 
  group_by(experiment, condition, grammatical, verb_num, attracted) %>%
  summarize(avRT = mean(RT), p_yes = mean(ResponseYes, na.rm = T)) %>% 
  as.data.frame()

dataAv %>% ggplot(aes(grammatical, p_yes, group = paste(experiment,attracted), color = experiment )) + geom_point() + geom_line(aes(linetype =attracted))

data$trial_group <- Hmisc::cut2(data$trial_no, g=5)

dataAvSplit <- data %>% 
  group_by(experiment, condition, grammatical, verb_num, attracted, trial_group) %>%
  summarize(avRT = mean(RT), p_yes = mean(ResponseYes, na.rm = T)) %>% 
  as.data.frame()

plot_split <- dataAvSplit %>% ggplot(aes(grammatical, p_yes, group = paste(experiment,attracted), color = experiment )) + geom_point() + geom_line(aes(linetype =attracted)) + facet_wrap(~trial_group)

dataAvBySubj <- data %>% 
  group_by(Subject, experiment, condition, grammatical, verb_num, attracted) %>%
  summarize(avRT = mean(RT), p_yes = mean(ResponseYes, na.rm = T), N = sum(!is.na(ResponseYes))  )  %>% 
  as.data.frame()
head(dataAvBySubj,10)

dataAvBySubjWide = dataAvBySubj %>% mutate(expcond = paste(experiment,condition, sep="_")) %>% dplyr::select(-experiment, -condition, -avRT, -N, -grammatical, -verb_num, -attracted) %>% tidyr::spread(expcond, p_yes)
dataAvBySubjWide %<>% mutate(delta_dc = AgrAttr_d - AgrAttr_c)
bad_subjects = subset(dataAvBySubjWide, delta_dc <= 0.25 ) %>% .$Subject

dataAvBySubj %>% subset(Subject %in% bad_subjects) %>% ggplot(aes(grammatical, p_yes, group = paste(experiment,attracted), color = experiment )) + geom_point() + geom_line(aes(linetype =attracted)) + facet_wrap(~Subject)

dataAvClean <- data %>% subset(!Subject %in% bad_subjects)%>% 
  group_by(experiment, condition, grammatical, verb_num, attracted) %>%
  summarize(avRT = mean(RT), p_yes = mean(ResponseYes, na.rm = T)) %>% 
  as.data.frame()

dataAvClean <- slice(dataAvClean, 1:4)

plot_average <- dataAvClean %>% ggplot(aes(grammatical, p_yes, group = paste(experiment,attracted), color = experiment )) + geom_point() + geom_line(aes(linetype =attracted)) #+ facet_wrap(~experiment, scales = "free_y")

@@

\vspace{2mm}\hrule

@@

\bleft

@@

@@

# REPLICATON OF LAGO ET AL. (2018)

In their study, @Lago investigate the comprehension of subject-verb agreement in Turkish-German bilinguals and Turkish monolinguals. They use speeded acceptability judgments for the effects of number attraction in Turkish. Their sentences make us of genitive-possessive constructions in the subject position, where the genitive is the attractor and the possessive is the head noun. They manipulate the grammaticality of the sentence by changing the plural morphology of the verb, and they also manipulate the plurality of the attractor noun. In grammatical conditions, the subject and the verb both bear singular morphology with no overt morpheme. Moreover, in the ungrammatical conditions, the verb bears the overt *-lAr* morpheme whereas the subject is still singular as exemplified below.

\begin{exe}
\ex
\begin{xlist}
\ex \underline{Grammatical, SG attractor} \label{lago1}
\gll \c{S}ark{\i}c{\i}-n{\i}n vokalist-i sahne-de s\"{u}rekli z{\i}pla-d{\i}\\
singer-\textsc{gen} vocalist-\textsc{poss} stage-\textsc{loc} non-stop jump-\textsc{pst}-$\varnothing$\\
\glt The singer's backup vocalist jumped on the stage non-stop.

\ex \underline{Grammatical, PL attractor} \label{lago2}
\gll \c{S}ark{\i}c{\i}-lar-{\i}n vokalist-i sahne-de s\"{u}rekli z{\i}pla-d{\i}\\
singer-\textsc{pl}-\textsc{gen} vocalist-\textsc{poss} stage-\textsc{loc} non-stop jump-\textsc{pst}-$\varnothing$\\
\glt The singers' backup vocalist jumped on the stage non-stop.

\ex \underline{Ungrammatical, PL attractor} \label{lago3}
\gll \c{S}ark{\i}c{\i}-lar-{\i}n vokalist-i sahne-de s\"{u}rekli z{\i}pla-d{\i}-lar.\\
singer-\textsc{pl}-\textsc{gen} vocalist-\textsc{poss} stage-\textsc{loc} non-stop jump-\textsc{pst}-\textsc{3Pl}\\
\glt The singers' backup vocalist jumped on the stage non-stop.

\ex \underline{Ungrammatical, SG attractor} \label{lago4}
\gll \c{S}ark{\i}c{\i}-n{\i}n vokalist-i sahne-de s\"{u}rekli z{\i}pla-d{\i}-lar.\\
singer-\textsc{gen} vocalist-\textsc{poss} stage-\textsc{loc} non-stop jump-\textsc{pst}-\textsc{3Pl}\\
\glt The singer's backup vocalist jumped on the stage non-stop.
\end{xlist}
\end{exe}

@@

\begin{exe}
\ex
\begin{xlist}
\ex \underline{Grammatical, SG attractor} \label{exp1}
\gll Komedyen-in yard{\i}mc{\i}-s{\i} poyraz-dan dolayi \"{u}\c{s}\"{u}-d\"{u}.\\
comedian-\textsc{gen} helper-\textsc{poss} northeaster-\textsc{abl} because.of feel.chilly-\textsc{pst}-$\varnothing$\\
\glt Because of the northeaster, comedian's assistant felt chilly.

@@

\ex \underline{Ungrammatical, PL attractor} \label{exp3}
\gll Komedyen-ler-in yard{\i}mc{\i}-s{\i} poyraz-dan dolayi \"{u}\c{s}\"{u}-d\"{u}-ler.\\
comedian-\textsc{pl}-\textsc{gen} helper-\textsc{poss} northeaster-\textsc{abl} because.of feel.chilly-\textsc{pst}--\textsc{pl}\\
\glt Because of the northeaster, comedians' assistant felt chilly.

@@

@@

In \textsc{Figure} (1), the y-axis shows the percentage of "acceptable" answers, and the x-axis indicates whether or not the sentences in that group are grammatical. Moreover, the linet ypes indicate an attractor noun with overt plural morphology. As seen in the figure, `r round(100*dataAvClean[1,7])`% of the sentences with plural attractors and a singular verb were accepted by the participants, in line with the findings of @Lago. We also see a number attraction rate of `r round(100*(dataAvClean[1,7]-dataAvClean[3,7]))`% which was also observed in @Lago with close results.

@@

And yes, I plan to beautify the figures.
\begin{figure}[H]
  \begin{floatrow}
    \ffigbox{%
```{r, fig.width = 4 , fig.height = 4 , fig.align = "right", echo = F}
print(plot_average)
```
    }{\caption{A figure}}

    \btabbox{%
```{r, fig.align = "right", echo = F}

```
    }{\caption{A table}}
  \end{floatrow}
\end{figure}

@@

In this paper, we have entertained the idea of task effect in the so-called Turkish number attraction phenomenon. We argue that the findings of the @Lago study is not clear and there are too many variables to account for in the experiment, one of them being the ambiguous morphology that the head noun bears. In the first experiment, we have replicated the attraction task of @Lago. We have found the similar effects of agreement with a bigger pool of participants. Then, for entertaining the other possibility in which we argue that participants do not fully reconstruct the sentence; however, they make us of the direct cue of overt morpheme *-lAr*, we offer an experiment where we use object relative clauses as an attractor.

# ACKNOWLEDGEMENTS
We used the statistical language `R` `r citep(citation())` for all our analyses. These were implemented in dynamic rmarkdown documents using `knitr` `r citep(citation("knitr"))` and `rmarkdown` `r citep(citation("rmarkdown"))` packages. All graphs have been done with `ggplot` `r citep(citation("ggplot2"))`. We also would like to thank Mine Nakipo\u{g}lu and Kadir Gökgöz for giving us the oppurtunity to conduct experiments and having participants from their classes.

@@

```{r write_citations, cache=FALSE, include=FALSE}
write.bibtex(file="knitcitations.bib")
```

<div id = "refs"></div>

\eleft

\listoftables

\listoffigures

```{r sessioninfo, echo = FALSE, eval = FALSE}
# set eval = FALSE if you don't want this info (useful for reproducibility) to appear 
sessionInfo()
```

>>>>

author: 
  - name          : "Utku Türk"
    affiliation   : "1"
    corresponding : yes    # Define only one corresponding author
    address       : "Postal address"
    email         : "utku.turk@boun.edu.tr"
  - name          :  "Pavel Logačev"
    affiliation   : "1"
affiliation       :
  - id            : "1"
    institution   : "Boğaziçi University University, Istanbul, Turkey"

authornote: |
  Add complete departmental affiliations for each author here. Each new line herein must be indented, like this line.
  Enter author note here.
shorttitle: Why Utku is the best
abstract: |
  This paper deals with agreement attraction because it's more important than literally anything else.
  Recently, Lago et al. (2018) demonstrated agreement attraction effects in comprension in Turkish, which is super-interesting because this finding allows us to make a lot of money. However, there is an alternative explanation for their findings: dark sorcery. In this paper we tested the predictions of these alternative accounts. In Experiment 1, we found that a particular kind of dark sorcery was not involved. In Experiment 2, we shall find ...

keywords          : "keywords"
wordcount         : "X"
bibliography      : ["myreferences.bib", "references.bib"]
floatsintext      : no
figurelist        : no
tablelist         : no
footnotelist      : no
linenumbers       : no
mask              : no
draft             : no
documentclass     : "apa6"
classoption       : "doc"
output            : 
  papaja::apa6_pdf:
    includes:
        in_header: header.tex
editor_options: 
  chunk_output_type: console
---

<!--  - knitcitations.bib

-->

```{r setup, eval =T, include = FALSE, message=FALSE, warning=FALSE}
library("papaja")
library(knitcitations)
library(tidyverse)
library(magrittr)
library(ggplot2)
theme_set(theme_bw())

library(car, warn.conflicts = FALSE)
library(MASS)
library(brms)
library(xtable)
library(ggpubr)

library(languageR)
library(tidyverse)
library(gdata)
library(MASS)
library(magrittr)
library(ggplot2)

source("../scripts/misc.R")

@@

```{r analysis-preferences, eval =T, message=FALSE, warning=FALSE}
# Seed for random number generation
set.seed(42)
knitr::opts_chunk$set(encoding = 'UTF-8',
                      cache.extra = knitr::rand_seed,
                      echo = FALSE,
                      results = 'hide')
options("citation_format" = "pandoc")

@@

<!--
\vspace{2mm}\hrule

@@

@@

-->

@@

# Experiment 1

```{r loadDataExp1, message=FALSE, warning=FALSE, include=FALSE, paged.print=FALSE}

fname_data <- "../workspace_exp1/exp_data.rds"
data <- readRDS(file = fname_data)

# compute by-subject percentages of 'yes' responses, and average RTs 
avg_by_subj <- data %>%
                group_by(subject, experiment, condition, 
                         grammatical, verb_num, attractor_num) %>%
                summarize(avRT = mean(RT), 
                          p_yes = mean(ResponseYes, na.rm = T), 
                          N = sum(!is.na(ResponseYes))  )

# reformat by-subject averages to a wide format
avg_by_subj_wide <- avg_by_subj %>% 
                      mutate(expcond = paste(experiment, condition, sep="_")) %>% 
                      ungroup() %>%
                      dplyr::select(-experiment, -condition, -avRT, -N,
                                    -grammatical, -verb_num, -attractor_num) %>%
                      tidyr::spread(expcond, p_yes) %>% 
                      mutate(delta_dc = AgrAttr_d - AgrAttr_c)

```{r loadDataLago, message=FALSE, warning=FALSE, include=FALSE, paged.print=FALSE}

# Load Lago et al.'s monolingual data
fname_lagoetal <- "../Data/Lago_et_al/Lago_data.csv"
df_lagoetal <- read.csv(fname_lagoetal, encoding = "UTF-8", as.is = T)
df_lagoetal %<>% subset(Group == "monolingual")
df_lagoetal %<>% dplyr::select(-Accuracy, -L1:-Group, -List:-SelfRateGerman)

# Note: All rows with Experiment == "offline" also seem to be for 
#       the UNP task ('Grammatical' is NA). I wonder if these were
#       the same subjects, or if the subject labels were simply the same
#       for the two experiments.
with(df_lagoetal, stopifnot( is.na(Grammatical) == (Experiment == "offline") ))

df_lagoetal_unp <- df_lagoetal %>% 
                    subset(is.na(Grammatical)) %>%
                    dplyr::select(-Grammatical:-Label)
df_lagoetal_attr <- df_lagoetal %>% 
                  subset(!is.na(Grammatical)) %>%
                  dplyr::select(-Distance:-NewCond)

In their study, @Lago investigates the comprehension of subject-verb agreement  Turkish monolinguals. They use speeded acceptability judgments for the effects of number attraction in Turkish. Their sentences make us of genitive-possessive constructions in the subject position, where the genitive is the attractor and the possessive is the head noun. They manipulate the grammaticality of the sentence by changing the plural morphology of the verb, and they also manipulate the plurality of the attractor noun. In grammatical conditions, the subject and the verb both bear singular morphology with no overt morpheme. Moreover, in the ungrammatical conditions, the verb bears the overt *-lAr* morpheme whereas the subject is still singular as exemplified below.

\begin{exe}
\ex
\begin{xlist}

\ex \textsc{Ungrammatical, SG attractor} \label{lago4}
\gll \c{S}ark{\i}c{\i}-n{\i}n vokalist-i sahne-de s\"{u}rekli z{\i}pla-d{\i}-lar.\\
singer-\textsc{gen} vocalist-\textsc{poss} stage-\textsc{loc} non-stop jump-\textsc{pst}-\textsc{3Pl}\\
\glt The singer's backup vocalist jumped on the stage non-stop.

\ex \textsc{Grammatical, PL attractor} \label{lago2}
\gll \c{S}ark{\i}c{\i}-lar-{\i}n vokalist-i sahne-de s\"{u}rekli z{\i}pla-d{\i}\\
singer-\textsc{pl}-\textsc{gen} vocalist-\textsc{poss} stage-\textsc{loc} non-stop jump-\textsc{pst}-$\varnothing$\\
\glt The singers' backup vocalist jumped on the stage non-stop.

\ex \textsc{Ungrammatical, PL attractor} \label{lago3}
\gll \c{S}ark{\i}c{\i}-lar-{\i}n vokalist-i sahne-de s\"{u}rekli z{\i}pla-d{\i}-lar.\\
singer-\textsc{pl}-\textsc{gen} vocalist-\textsc{poss} stage-\textsc{loc} non-stop jump-\textsc{pst}-\textsc{3Pl}\\
\glt The singers' backup vocalist jumped on the stage non-stop.

\ex \textsc{Grammatical, SG attractor} \label{lago1}
\gll \c{S}ark{\i}c{\i}-n{\i}n vokalist-i sahne-de s\"{u}rekli z{\i}pla-d{\i}\\
singer-\textsc{gen} vocalist-\textsc{poss} stage-\textsc{loc} non-stop jump-\textsc{pst}-$\varnothing$\\
\glt The singer's backup vocalist jumped on the stage non-stop.

@@

\begin{exe}
\ex
  \begin{xlist}
  \ex \underline{Ungrammatical, PL attractor} \label{exp3}
      \gll Komedyen-ler-in yard{\i}mc{\i}-s{\i} poyraz-dan dolayi \"{u}\c{s}\"{u}-d\"{u}-ler.\\
  comedian-\textsc{pl}-\textsc{gen} helper-\textsc{poss} northeaster-\textsc{abl} because.of feel.chilly-\textsc{pst}--\textsc{pl}\\
      \glt Because of the northeaster, comedians' assistant felt chilly.

@@

@@

  \ex \underline{Grammatical, SG attractor} \label{exp1}
      \gll Komedyen-in yard{\i}mc{\i}-s{\i} poyraz-dan dolayi \"{u}\c{s}\"{u}-d\"{u}.\\
  comedian-\textsc{gen} helper-\textsc{poss} northeaster-\textsc{abl} because.of feel.chilly-\textsc{pst}-$\varnothing$\\
      \glt Because of the northeaster, comedian's assistant felt chilly.

@@

```{r identifyBadSubjects, eval =T, message=FALSE, warning=FALSE, include=FALSE, paged.print=FALSE}

# identify participants 
bad_subjects <- subset(avg_by_subj_wide, delta_dc <= 0.25 ) %>% .$subject

#dataAvBySubj %>% subset(subject %in% bad_subjects) %>% ggplot(aes(grammatical, p_yes, group = paste(experiment,attracted), color = experiment )) + geom_point() + geom_line(aes(linetype =attracted)) + facet_wrap(~subject)

data_clean <- data %>% subset(!subject %in% bad_subjects)

In \textsc{Figure} (1), the y-axis shows the percentage of "acceptable" answers, and the x-axis indicates whether or not the sentences in that group are grammatical. Moreover, the linet ypes indicate an attractor noun with overt plural morphology. As seen in the figure, `r 1`% of the sentences with plural attractors and a singular verb were accepted by the participants, in line with the findings of @Lago. We also see a number attraction rate of `r 2`% which was also observed in @Lago with close results.

@@

```{r mergeData, eval =T, message=FALSE, warning=FALSE, include=FALSE, paged.print=FALSE}

df_merge_exp1 <- data_clean %>% ungroup() %>% 
                      dplyr::select(source=experiment, grammatical, attractor_num, # condition,
                                    subject, item=Item,
                                    ResponseYes, RT)
df_merge_exp1$experiment <- "Experiment 1"
df_merge_exp1$grammatical <- with(df_merge_exp1, ifelse(grammatical == "gram", 
                                                        "grammatical",
                                                        "ungrammatical"))
df_merge_exp1$attractor_num <- with(df_merge_exp1, ifelse(attractor_num == "pl", 
                                                          "plural", 
                                                          "singular"))
df_merge_exp1$item %<>% as.integer()
df_merge_exp1$subject %<>% as.character()

df_lagoetal_attr %<>% mutate(ResponseYes = (Response == "yes") )
df_merge_lago <- df_lagoetal_attr %>% ungroup() %>% 
                      dplyr::select(grammatical=Grammatical, attractor_num=Attractor, #condition=Condition, 
                                    subject=Participant, item=Item,
                                    ResponseYes, RT)
df_merge_lago$experiment <- "Lago et al. (2018)" 
df_merge_lago$source <- NA
df_merge_lago$item %<>% add(1000)

df_merged <- dplyr::bind_rows(df_merge_exp1, df_merge_lago)
df_merged$subject %<>% as.factor()
df_merged$item %<>% as.factor()
```

```{r computeAverages, eval =T, message=FALSE, warning=FALSE, include=FALSE, paged.print=FALSE}

avg_clean <- df_merged %>%
                group_by(experiment, source, grammatical, attractor_num) %>%
                summarize(avgRT = mean(RT), p_yes = mean(ResponseYes, na.rm = T))
```

## Responses

```{r exp1AvgResponse, fig.height = 2.5, fig.width = 6, fig.cap="Estimates and 95% credible intervals for the analysis of the probability of a 'yes' response."}

avg_exp <- avg_clean %>% subset(is.na(source) | source != "filler")
avg_fillers <- avg_clean %>% subset(source == "filler")

p_avg_resp <- ggplot(avg_exp, 
                     aes(grammatical, p_yes, #linetype = attractor_num, 
                         color = attractor_num, group = attractor_num)) + 
                geom_point() + geom_line() + 
                facet_wrap(~experiment)

p_avg_resp <- p_avg_resp + geom_line(data = avg_fillers) + geom_point(data = avg_fillers)

print(p_avg_resp)

```{r exp1ModelResponse, eval = F}

# # TODO: the following subjects have too much data: 11, 28, 36, 42, 55, 65, 73, 84, 92, 
# #
# x <- df_merged %>% subset(experiment == "Experiment 1") %>% group_by(subject) %>% dplyr::summarize(F = sum(is.na(attractor_num)),
#                                                           N = length(is.na(attractor_num)) )
# x %>% as.data.frame()
# 
# x$N %>% sum()
# x$F %>% sum()

#summary(as.factor(df_merged$attractor_num))

df_merged %<>% within(., {
  cGrammatical <- ifelse(grammatical == "grammatical", .5, -.5)
  cUngrammatical <- ifelse(grammatical == "ungrammatical", .5, -.5)
  cAttractorPlural <- ifelse(attractor_num == "plural", .5, -.5)
  cEndsInVowel <- ifelse(experiment == "Experiment 1", .5, -.5)
})
df_merged_nofillers <- df_merged %>% subset(is.na(source) | source != "filler")

# ## test model parameterization using a simple GLM first
# m <- glm(ResponseYes ~ cEndsInVowel * cUngrammatical * cAttractorPlural,
#          data = df_merged_nofillers,
#          family = binomial("probit"))
# summary(m)

n_chains <- 4
n_cores <- 4
n_iter <- 5000

fname_exp1_responses <- "../workspace_exp1/model_responses"

library(brms)

m_responses <- brm(ResponseYes ~ cEndsInVowel * cUngrammatical * cAttractorPlural + 
                                 (cUngrammatical * cAttractorPlural + 1| subject) +
                                 (cUngrammatical * cAttractorPlural + 1| item),
                   data = df_merged_nofillers,
                   family = bernoulli("probit"),
                   file = fname_exp1_responses, 
                   chains = n_chains, cores = n_cores, iter = n_iter)

```{r exp1ResponseModelPlot, eval = F, fig.height= 1.5, message=FALSE, warning=FALSE, fig.cap="Estimates and 95% credible intervals for the analysis of the probability of a 'yes' response."}

contrast_names <- c("cUngrammatical" = "Ungrammaticality",
                    "cAttractorMatch" = "Attactor Match",
                    "cUngrammatical:cAttractorMatch" = "Ungrammaticality * Attractor Match")

p_m_response <- create_model_coefs_plot(m_responses, map_names = contrast_names)
p_m_response <- p_m_response + xlab("Estimate (log-odds)")
print(p_m_response)

## Response Times

```{r exp1AvgRTs, fig.height=2.5, fig.width = 6 }

p_avg_rt <- ggplot(avg_clean, aes(grammatical, avgRT, linetype = attractor_num, color = experiment, group = paste(experiment, attractor_num))) + geom_point() + geom_line()

print(p_avg_rt)

@@

In this paper, we have entertained the idea of task effect in the so-called Turkish number attraction phenomenon. We argue that the findings of the @Lago study is not clear and there are too many variables to account for in the experiment, one of them being the ambiguous morphology that the head noun bears. In the first experiment, we have replicated the attraction task of @Lago. We have found the similar effects of agreement with a bigger pool of participants. Then, for entertaining the other possibility in which we argue that participants do not fully reconstruct the sentence; however, they make us of the direct cue of overt morpheme *-lAr*, we offer an experiment where we use object relative clauses as an attractor. 
-

# ACKNOWLEDGEMENTS
We used the statistical language `R` `r citep(citation())` for all our analyses. These were implemented in dynamic rmarkdown documents using `knitr` `r citep(citation("knitr")[1])` and `rmarkdown` `r citep(citation("rmarkdown")[2])` packages. All graphs have been done with `ggplot` `r citep(citation("ggplot2"))`.

@@

```{r write_citations, eval =T, cache=FALSE, include=FALSE}
write.bibtex(file="references.bib")
```
